The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-07-27 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
    \centering
    \includegraphics{figures/delay_time_distributions.pdf}
    \caption{Models of the SN Ia delay time distribution used in this paper. All functions are normalized to $f_{\rm Ia}=1$ at $\tau=1$ Gyr.}
    \label{fig:dtds}
    \script{delay_time_distributions.py}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/feh_df_sfh.pdf}
    \caption{Distributions of [Fe/H] from multi-zone simulations with different SFHs. The plot format is similar to Figure \ref{fig:feh-df-dtd}. In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed. Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
    \label{fig:feh-df-sfh}
    \script{feh_df_sfh.py}
\end{figure*}
\subsection{The distribution of [O/Fe]}

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/delay_time_distributions.pdf}
    \caption{Models of the SN Ia delay time distribution used in this paper. All functions are normalized to $f_{\rm Ia}=1$ at $\tau=1$ Gyr. The black squares represent the DTD recovered for the SDSS-II sample of SNe Ia by \citet{Maoz2012-SloanIIDTD}. The horizontal error bars indicate the time range of each DTD measurement, and the vertical error bars represent the 1$\sigma$ uncertainties.}
    \label{fig:dtds}
    \script{delay_time_distributions.py}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/feh_df_sfh.pdf}
    \caption{Distributions of [Fe/H] from multi-zone simulations with different SFHs. The plot format is similar to Figure \ref{fig:feh-df-dtd}. In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed. Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
    \label{fig:feh-df-sfh}
    \script{feh_df_sfh.py}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics{figures/feh_df_comparison.pdf}
    \caption{Distributions of [Fe/H] from multi-zone simulations with different SFHs. The plot format is similar to Figure \ref{fig:feh-df-dtd}. In all cases an exponential DTD with timescale $\tau=1.5$ Gyr is assumed. Distributions from APOGEE DR17, binned and smoothed similarly, are presented in the right-most column for reference.}
    \label{fig:feh-df-comparison}
    \script{feh_df_comparison.py}
\end{figure*}

\subsection{The distribution of [O/Fe]}
